Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/experiments.tex
small fixes

% We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the
% explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
%We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}). 
\eva{What are the 'underlying computations'? Isn't this supposed to go into the
implementation section of Section 5?}
For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller
consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
For the aircraft model, Matlab computes a robust EMPC with
$27$ regions and $217$ 4D hyperplanes for most values of $\varepsilon_Q$ and $\Delta$. 
The only exception is when $\Delta=0.30$
and $\varepsilon_Q=0.001$ for which we get $26$ regions having $208$ hyperplanes.
In general, we expect that increasing $\Delta$ results in shrinking of feasible
set size.

@@

The benchmark in this experiment is the double integrator, a canonical example
of a second order control system \todo{cite something?}. The state space description
for the discrete time version of the double integrator is given by:
\begin{equation}
x_{k+1}=
\begin{bmatrix}
1 & T_s\\
0& 1	
\end{bmatrix}
x_k+
\begin{bmatrix}
0\\
T_s
\end{bmatrix}u_k
\label{eq:int2_ss}
\end{equation}
where, $T_s=0.1$ is the sample time. The state and input constraints are
\begin{align*}
	\begin{bmatrix}
		-5\\-5
	\end{bmatrix}\leq&
	x_k\leq
	\begin{bmatrix}
	5\\5
	\end{bmatrix}, \quad
	-1\leq u_k \leq 1
\end{align*}%}
%\eva{More details about this + citation}

>>>>

% We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the
% explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
%We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.

For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller
consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
For the aircraft model, Matlab computes a robust EMPC with
$27$ regions and $217$ 4D hyperplanes for most values of $\varepsilon_Q$ and $\Delta$. 
The only exception is when $\Delta=0.30$
and $\varepsilon_Q=0.001$ for which we get $26$ regions having $208$ hyperplanes.
In general, we expect that increasing $\Delta$ results in shrinking of feasible
set size.

@@

The benchmark in this experiment is the double integrator, a canonical example
of a second order control system. The state space description
for the discrete time version of the double integrator is given by:
\begin{equation}
x_{k+1}=
\begin{bmatrix}
1 & T_s\\
0& 1	
\end{bmatrix}
x_k+
\begin{bmatrix}
0\\
T_s
\end{bmatrix}u_k
\label{eq:int2_ss}
\end{equation}
where, $T_s=0.1$ is the sample time. The state and input constraints are
\begin{align*}
	\begin{bmatrix}
		-5\\-5
	\end{bmatrix}\leq&
	x_k\leq
	\begin{bmatrix}
	5\\5
	\end{bmatrix}, \quad
	-1\leq u_k \leq 1
\end{align*}%}
%\eva{More details about this + citation}

### 2019-04-12 emsoft-2019/intro.tex
small fixes

However, there are still bottlenecks in implementing explicit MPC on resource-constrained embedded micro-controllers.
First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
problem can involve many (often hundreds) of regions. \todo{citation for such example, e.g. the double integrator}
Since the memory consumption grows linearly with the number of regions, 
this can be a limiting factor in using explicit MPC on resource-constrained micro-controllers.
Second, many low-end micro-controllers only support fixed-point arithmetic.
Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable~\cite{Anta10}. 
An implementation of explicit MPC has to be \emph{robust} to 
implementation errors to be able to enforce hard constraints on the states at run time~\cite{imperialrmpc}.

>>>>

However, there are still bottlenecks in implementing explicit MPC on resource-constrained embedded micro-controllers.
First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
Since the memory consumption grows linearly with the number of regions, 
this can be a limiting factor in using explicit MPC on resource-constrained micro-controllers.
Second, many low-end micro-controllers only support fixed-point arithmetic.
Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable~\cite{Anta10}. 
An implementation of explicit MPC has to be \emph{robust} to 
implementation errors to be able to enforce hard constraints on the states at run time~\cite{imperialrmpc}.
